We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-15 paper/paper.tex
edit

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
We build up on the suggestions made in \cite{2017AN....338..854P}, 
focusing on asphericity estimates for a fixed number of the brightest
satellites around each galaxy.
In the interest of keeping the method straightforward and robust we do
not look for planes in subsets of satellites or coherent kinematical
structures.

The method uses as a reference point the spherically randomized data
of the system under study.
We first measure the width and axis ratios for the satellite
distributions of interest. 
Then, we measure the same quantities for the same set of points after
a process of spherical randomization.
Finally, we renormalize the initial results to the mean value and
standard deviation computed from the randomized data.

The normalized quantities for different systems are well reproduced by
a multivariate gaussian distribution. 
We fit the parameters of this gaussian to the results from 
LG samples coming from three different simulations
to finally compare the observational results against the distributions
derived from the simulations.

>>>>

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the around the MW and M31.  
In the interest of keeping the method straightforward and robust we do
not look for planes in subsets of satellites or coherent kinematical
structures. 
We focus on the asphericity estimates for a fixed number of the
brightest satellites around each galaxy.

The method uses as a reference the spherically randomized data
of the system under study \citep{2017AN....338..854P}.  
To this end, we first measure the width and axis ratios for the satellite
distributions of interest. 
Then, we measure the same quantities for the same set of points after
a process of spherical randomization.
Finally, we renormalize the initial results to the mean value and
standard deviation computed from the randomized data.

We find that these normalized quantities are well described by
a multivariate gaussian distribution. 
We fit estimate the mean and covariance of this distributions using
the results of LG pairs coming from three different numerical
simulations, we inally compare the observational results against the
distributions derived from the simulations: Illustris-1,
Illustris-1-Dark and ELVIS.
